### 2019-09-13 README.Rmd
working on escape bug in kables
This escape is a bug that has to do with either R or pandoc version. Works from iMac

```{r get_kegg_kable, warning=FALSE, echo=FALSE, message=FALSE}
if (require(kableExtra)){
knitr::kable(kegg_df, format = 'html',escape = FALSE,
             caption = "Table 1. Description of data sets generated from accessing KEGG REST API", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
}
```

>>>>

```{r get_kegg_kable, warning=FALSE, echo=FALSE, message=FALSE}
if (require(kableExtra)){
knitr::kable(kegg_df, escape = FALSE,
             caption = "Table 1. Description of data sets generated from accessing KEGG REST API", row.names = FALSE) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
}
```
